\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}

\input{../../Comments}
\input{../../Common}

\title{Usability Testing Survey\\\progname}

\author{\authname}

\date{}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
14 March 2025 & Sumanya Gulati & Initial Draft\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\section{User and Session Details}
Table \ref{UserDetails} contains details of each subject who agreed to participate in a 
Usability Testing Session.
\begin{table}[hp]
\begin{tabularx}{\textwidth}{l | X}
\toprule
\textbf{Subject Name} &  \\
\midrule
\textbf{Subject Role} &  \\
\midrule
\textbf{Test Conductor(s)} &  \\
\midrule
\textbf{Test Date} &  \\
\midrule
\textbf{Test Mode} &  \\
\midrule
\textbf{Start Time} &  \\
\midrule
\textbf{End Time} &  \\
\midrule
\textbf{Additional Notes} &  \\
\bottomrule
\end{tabularx}
\caption{User and Session Details} \label{UserDetails}
\end{table}

\section{User Answers}

Users will be asked the following questions to gauge the usability of the
application during a user demo assessment. These questions relate to
the assessment of non-functional tests NFR-LF1, NFR-UH1, NFR-OE2, and NFR-MS1 outlined in the 
\href{https://github.com/SumanyaG/Alkalytics/blob/main/docs/SRS/SRS.pdf}{Software Requirements Specification (SRS)}.

\subsection*{\textbf{Navigation and Ease of Use}}
  \begin{itemize}
    \item[(a)] How easy or difficult was it to navigate through the
    application? \textit{(Very easy - Somewhat easy - Neither easy nor difficult
    - Somewhat difficult - Very difficult)}
    \item \emph{Answer:}
    \item[(b)] Rate the ease of finding a specific button/feature related to the
    task you were trying to perform. \textit{(Very easy - Somewhat easy -
    Neither easy nor difficult - Somewhat difficult - Very difficult)}
    \item \emph{Answer:}
  \end{itemize}

\subsection*{\textbf{Visual Appearance}}
  \begin{itemize}
    \item[(a)] On a scale of 1 to 5, how would you rate the visual appearance of
    the application? \textit{(1 - Too cluttered and unappealing, 2 - Somewhat
    unappealing 3 - Neutral, 4 - Somewhat appealing, 5 - Very clean and
    appealing)}
    \item \emph{Answer:}
    \item[(b)] Is the displayed content (text, tables, graphs) clear, legible
    and easy to understand?
    \item \emph{Answer:}
    \item[(c)] Did the design and layout appear consistent to you across
    the entire application? If no, please point out any inconsistencies you noticed.
    \item \emph{Answer:}
    \item[(d)] Did you encounter any unidentifiable symbols or icons? If yes,
    please describe them.
    \item \emph{Answer:}
  \end{itemize}

\subsection*{\textbf{Learning}}
  \begin{itemize}
    \item[(a)] How easy or difficult was it to learn how to use the different
    features of the application? \textit{(Very easy - Somewhat easy - Neither
    easy nor difficult - Somewhat difficult - Very difficult)}
    \item \emph{Answer:}
    \item[(b)] Were there any features or functions you found challenging to
    understand or figure out? If yes, please describe. 
    \item \emph{Answer:}
  \end{itemize}

\subsection*{\textbf{Responsiveness}}
  \begin{itemize}
    \item[(a)] Did you experience any noticeable delays or interruptions while
    using the application? If yes, please describe them.
    \item \emph{Answer:}
  \end{itemize}

\subsection*{\textbf{Overall Experience}}
  \begin{itemize}
    \item[(a)] On a scale of 1 to 5, rate your overall experience using the
    application. \textit{(1 - Very poor, 2 - Poor, 3 - Neutral, 4 - Good, 5 -
    Excellent)}
    \item \emph{Answer:}
    \item[(b)] Do you have any suggestions for improvements to enhance your
    experience with the application?
    \item \emph{Answer:}
  \end{itemize}

\end{document}