\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

The following objectives have been derived from Section 9 of the
\href{https://github.com/SumanyaG/Alkalytics/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{Development
Plan} and describe what will be demonstrated during the team's Proof of
Concept Demonstration.
\begin{itemize}
  \item Developing and implementing a migration algorithm for transferring CSV
  data files to the database. 
  \item Ensuring that 100\% of the existing data has been migrated  without loss
  or error to the new database.
  \item Demonstrating that all existing inter-parameter comparisons in the Excel
  templates have been replicated in the database.
\end{itemize}

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 9\\
Sumanya Gulati & 9\\
Jennifer Ye & 9\\
Jason Tran & 9\\
Kate Min & 9\\
\bottomrule
\end{tabular}
\end{table}

All team members attended every team meeting during the time period of interest.

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Sumanya Gulati & 5\\
Jennifer Ye & 4\\
Jason Tran & 4\\
Kate Min & 4\\
\bottomrule
\end{tabular}
\end{table}

One of the five supervisor meetings involved a tour of the lab and the
apparatus, in which Sumanya attended alone due to differences in availability.
The total count of five supervisor meetings is fewer than the expected meeting
frequency established in Section 4.2 of the
\href{https://github.com/SumanyaG/Alkalytics/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{Development
Plan} for the following reasons:
\begin{enumerate}
	\item Meetings with Dr. de Lannoy's participation were not strictly
	necessary as he is able to receive progress updates from Bassel, the
	secondary supervisor, and has been reviewing the team's deliverables sent
	via email. 
	\item There were no significant updates/questions during the weeks of
	October 8, October 15, and October 22 that would have necessitated a
	meeting; instead, some discussions were conducted via email.
\end{enumerate}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 12\\
Sumanya Gulati & 2\\
Jennifer Ye & 1\\
Jason Tran & 0\\
Kate Min & 1\\
\bottomrule
\end{tabular}
\end{table}

Due to the busy schedules of the team, one member may attend lectures on behalf
of the team. The number of attended lectures should be more, however the issues
to be created for later lectures were forgotten. The numbers in the table are soley
based on the number of issues created. The team will work to add
issues for lectures in the future. 

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{TA Discussions}\\
\midrule
Total & 4\\
Sumanya Gulati & 4\\
Jennifer Ye & 4\\
Jason Tran & 4\\
Kate Min & 4\\
\bottomrule
\end{tabular}
\end{table}

All members have attended all meetings with the TAs.

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 40 & 100\% \\
Jason Tran & 5 & 12.5\% \\
Jennifer Ye & 6 & 15\% \\
Kate Min & 8 & 20\% \\
Sumanya Gulati & 20 & 50\% \\
\bottomrule
\end{tabular}
\end{table}

As described in Section 7 - Workflow Plan of the 
\href{https://github.com/SumanyaG/Alkalytics/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{Development Plan},
in addition to creating separate branches for each milestone which which merged into the main
branch, each team member created a separate branch off of the milestone branch for their 
respective sections. Their commits from their section-specific milestone branches were squashed
into a single commit when merged to the milestone branch. Each of these squashed commits has been counted
singularly in the above table.\\
\newline
Additionally, the number of commits by Sumanya Gulati is over-represented in the count as 12/20 of the
commits are fixup! commits which were used to edit READMEs, upload relevant resources or fix minor 
formatting issues and such. These 12 commits do not reflect her contribution to the actual content of 
each milestone submission.

\section{Issue Tracker} \label{section:issue_tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Total & 103 & 87 \\
Jason Tran & 21 & 18 \\
Jennifer Ye & 4 & 13 \\
Kate Min & 3 & 20 \\
Sumanya Gulati & 62 & 36 \\
\bottomrule
\end{tabular}
\end{table}

We believe that the number of issues authored by each team member is not a fair
metric for our team. This is because for the first two milestones, all the issues
were opened and assigned to the respective members by the meeting chair for that
period (Sumanya Gulati in this instance).\\
\newline
After the submission of the \href{https://github.com/SumanyaG/Alkalytics/blob/main/docs/SRS/SRS.pdf}{SRS}
document, there was a brief transition period where every member opened their own issues
but post that transition period, the meeting chair for the current period (Jason Tran)
opened and assigned issues for all the team members.\\
\newline
We realize this is an inefficient system and so, for all upcoming milestones and
submissions, each team member will be responsible for opening and closing issues
for the sections and components assigned to them.

\section{CICD}

The initial phase of Continuous Integration (CI) has been implemented to our
project in the form of a \LaTeX build checker that flags any compiling issues
caused by incorrect syntax, missing elements or more.\\
\newline
As a part of the next phase of CI, we will be implementing linters, namely,
Flake8 and ESLint (as outlined in the 
\href{https://github.com/SumanyaG/Alkalytics/blob/main/docs/VnVPlan/VnVPlan.pdf}{Validation and Verification Plan}).
Additionally, we would continue using GitHub Actions to implement CI.

\section{Pull Requests}

\begin{table}[H]
	\centering
	\begin{tabular}{ll}
	\toprule
	\textbf{Student} & \textbf{Pull Requests (merged)} \\
	\midrule
	Total & 26 \\
	Jason Tran & 6 \\
	Jennifer Ye & 5 \\
	Kate Min & 7 \\
	Sumanya Gulati & 8 \\
	\bottomrule
	\end{tabular}
\end{table}

Although the total number of closed Pull Requests (PRs) is 32, only the 
ones that were successfully merged have been taken into account for the
above table. We believe that the number of PRs provides a much more
transparent and accurate representation of the contribution by each team
member as opposed to section \ref{section:issue_tracker}. 

\end{document}