% THIS DOCUMENT IS FOLLOWS THE VOLERE TEMPLATE BY Suzanne Robertson and James Robertson
% ONLY THE SECTION HEADINGS ARE PROVIDED
%
% Initial draft from https://github.com/Dieblich/volere
%
% Risks are removed because they are covered by the Hazard Analysis
\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,      % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\newcommand{\lips}{\textit{Insert your content here.}}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software} 
\author{\authname}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\textbf{Date}} & {\textbf{Version}} & {\textbf{Notes}}\\
\midrule
09-28-24 & 1.0 & Rough draft of sections 1,2,10,24\\
09-29-24 & 1.0.1 & Adds more content on sections 1,2,10,24 to further explain points\\
\bottomrule
\end{tabularx}

~\\

~\newpage
\section{Purpose of the Project}
\subsection{User Business}
This project aims to aid in the data management and analysis of an ocean
alkalinity enhancement experiment process. The research is working towards a
scalable process to capture CO\textsubscript{2} using a combination of electric
fields and membranes. The experiment's efficient generation process creates a
very dilute base. The product serves a niche solution, to rebalance the ocean's
PH levels to be able to absorb more CO\textsubscript{2}. As earth’s temperature
rises, so does the ocean’s, affects its PH balance. As this process is still on
a small scale, it is currently being perfected which means many more experiments
must be done to be able to bring it to a global scale. However, this requires a
massive production operation to do so. Optimization of the experimental data is
critical to improve process efficiency. This is a big data software problem
requiring the ability to find and fine-tune specific parameters. 
\subsection{Goals of the Project}
This platform will be able to consolidate and organize the data from the
experiments with proper labeling across all given data sets allowing for a
centralize method of data storage that is both scalable and maintainable. On the
platform users can request to see certain data points from anywhere from the
inputted data sets given any specified order. Once the data is returned to the
user the platform can show inter-parameter comparability to better aid data
analysis. This comparability acts as a starting point to analysis and is by no
means show a final analysis of the data. This will all be presented in a web
interface where all the user functions will be displayed and can be shared among
those involved in the experiment.   
\section{Stakeholders}

\subsection{Client}
Dr. Charles De Lannoy serves as the main client for this project as he is the
lead supervisor of the research study. This solution directly affects his work and
is intended to be a custom solution for the problem. Bassel Abdelkader is
another client of this project as he is the person that works directly with the
research data. One of his responsibilities is to record the experimental data and
upload them to their current data storage system, Microsoft Excel. 
\subsection{Customer}
Although this project is a tailored solution to one research study, its
application can be extended to any other situation where large sets of data is involved. 
This could be shared among other researchers to aid in their data management and analysis. 
\subsection{Other Stakeholders}
Current students and members of the lab working on the study is can also be
considered stakeholders for the same reasons as the clients. However, since they
will only be working with the study for a short amount of time without daily or
consistent interaction, they do not serve as a main stakeholder. The founder of
the study, who is currently funding the research project is another stakeholder.
However, since they do not work directly with the processes of the study rather
oversee the process, they may not have strong interest in the details of the solution. 
\subsection{Hands-On Users of the Project}
Potentially not applicable or useful for this document

\subsection{Personas}
\begin{itemize}
  \item John Doe is an 23 year old McMaster undergraduate student who has a
  research position on the ocean alkalinity research project. They have been
  tasked to aid the experiment data collection process. After being told that
  the data is being stored in a master Excel file; they find that is it hard to
  use. Being an engineering student without much experience with Excel, they
  struggle to find the data they want. Inputting data is still a manageable
  process but they find themselves to be spending a lot of time looking at Excel
  documentation which they find frustrating as that time could be allocated to
  being more productive during the school term. Although, they want to a better
  way to manage the data, they know that it is not up to their decision on what
  tools are being used but suggested that there could be another better solution
  to use. 
  \item Dr.\ Carly Kelvon is a 60 years old professor at a university and
  is working on her own research project for over five years. She has gathered
  lots of data and thankfully she has always been great at Excel. However, other
  the last two years she has found that Excel is becoming less sustainable. The
  queries are a lot slower and sifting through pages and pages of data is
  wasting a lot of her time. She sees this more evidently through those that
  work along side her as they are also facing the same struggles with even less
  Excel experience as her. She wants to find a more scalable solution but she
  fears that her lack of digital knowledge will do her more harm than good, as a
  result she fears that if she introduces a new platform to serve her needs
  better that she will find it hard and confusing to use. 
  \item Dr.\ Alex Stark is a 30 year old associate professor who has recently
  gotten funding for his innovative research idea and has been dedicating all
  his time on perfecting its methodology. It has only been one year since his
  research started but had recently found a great application of his ideas to
  reach far more people and be more impactful that he had originally thought.
  But with his current data management set up, he quickly realises that it is not
  sustainable. He finds that there are many other solutions on the market but
  they do not exactly meet his needs and cost a lot more than what he can spend
  on a tool. He decided that the best way is to create his own tool but lacks
  the software knowledge to create something stable and reliable. 
\end{itemize}
    
\subsection{Priorities Assigned to Users}
\subsubsection{Primary Users}
\begin{itemize}
  \item Dr. Charles De Lannoy
  \item Bassel Abdelkader
  \item Students working on the experiment 
\end{itemize}

\subsubsection{Secondary Users}
\begin{itemize}
  \item Researcher with their own research studies 
  \item The founder of the study
\end{itemize}
\subsection{User Participation}
Not a relevant section 
\subsection{Maintenance Users and Service Technicians}
Not a relevant section 

\section{Mandated Constraints}
\subsection{Solution Constraints}
\lips
\subsection{Implementation Environment of the Current System}
\lips
\subsection{Partner or Collaborative Applications}
\lips
\subsection{Off-the-Shelf Software}
\lips
\subsection{Anticipated Workplace Environment}
\lips
\subsection{Schedule Constraints}
\lips
\subsection{Budget Constraints}
\lips
\subsection{Enterprise Constraints}
\lips

\section{Naming Conventions and Terminology}
\subsection{Glossary of All Terms, Including Acronyms, Used by Stakeholders
involved in the Project}
\lips

\section{Relevant Facts And Assumptions}
\subsection{Relevant Facts}
\lips
\subsection{Business Rules}
\lips
\subsection{Assumptions}
\lips

\section{The Scope of the Work}
\subsection{The Current Situation}
\lips
\subsection{The Context of the Work}
\lips
\subsection{Work Partitioning}
\lips
\subsection{Specifying a Business Use Case (BUC)}
\lips

\section{Business Data Model and Data Dictionary}
\subsection{Business Data Model}
\lips
\subsection{Data Dictionary}
\lips

\section{The Scope of the Product}
\subsection{Product Boundary}
\lips
\subsection{Product Use Case Table}
\lips
\subsection{Individual Product Use Cases (PUC's)}
\lips

\section{Functional Requirements}
\subsection{Functional Requirements}
\lips

\section{Look and Feel Requirements}
All subitems in this sections are the fit criterion for its respective requirements. 
\subsection{Appearance Requirements}
\begin{itemize}
  \item [AR1.]The website should have a simple and organized layout, with
  clearly defined sections where all major functions should be easily accessible
  and viewable 
  \begin{itemize}
    \item[AR1.1] A users should be able to identify all the major
    functions of the website within five minuets of use.
  \end{itemize}
  \item [AR2.] The website shall be responsive on all computer and laptop screens
  aside from mobile screens
  \begin{itemize}
    \item [AR2.1] The usability of website should be the same
    as the default view on big and smaller computer, laptop and monitor screens
  \end{itemize}
  \item [AR3.] The website's functions and buttons shall be properly labeled
  where no button is ambiguous to users 
  \begin{itemize}
    \item [AR3.1] A user should be able to tell what all buttons inherently does
    without the needing to ask questions
  \end{itemize}
  \item [AR4.1]The produced plot from the data shall be properly labeled
  \begin{itemize}
    \item [AR4.1] The plots should not be ambiguous. Users should be able to understand
    what is the plot about within five minuets of viewing it.
  \end{itemize}
  \subitem
\end{itemize}

\subsection{Style Requirements}
\begin{itemize}
  \item [SR1.] All icons on the website must be in the artistic style
  \begin{itemize}
    \item [SR1.1] After a user's first encounter with the product, 90\% of users should
    see that there is unity among all the icons on the website. 
  \end{itemize}
  \item [SR2.] All colours must match the theme of the website
  \begin{itemize}
    \item [SR2.1] After a user's first encounter with the product, 80\% of users
    should agree that there is a common theme throughout the website.
  \end{itemize}
  \item [SR3.] All fonts are to be consistent throughout the website 
  \begin{itemize}
    \item [SR3.1] After a user's first encounter with the product, there should
    be no user who feels that any fonts do not belong on the website. 
  \end{itemize}
\end{itemize}

\section{Usability and Humanity Requirements}
\subsection{Ease of Use Requirements}
\lips
\subsection{Personalization and Internationalization Requirements}
\lips
\subsection{Learning Requirements}
\lips
\subsection{Understandability and Politeness Requirements}
\lips
\subsection{Accessibility Requirements}
\lips

\section{Performance Requirements}
\subsection{Speed and Latency Requirements}
\lips
\subsection{Safety-Critical Requirements}
\lips
\subsection{Precision or Accuracy Requirements}
\lips
\subsection{Robustness or Fault-Tolerance Requirements}
\lips
\subsection{Capacity Requirements}
\lips
\subsection{Scalability or Extensibility Requirements}
\lips
\subsection{Longevity Requirements}
\lips

\section{Operational and Environmental Requirements}
\subsection{Expected Physical Environment}
\lips
\subsection{Wider Environment Requirements}
\lips
\subsection{Requirements for Interfacing with Adjacent Systems}
\lips
\subsection{Productization Requirements}
\lips
\subsection{Release Requirements}
\lips

\section{Maintainability and Support Requirements}
\subsection{Maintenance Requirements}
\lips
\subsection{Supportability Requirements}
\lips
\subsection{Adaptability Requirements}
\lips

\section{Security Requirements}
\subsection{Access Requirements}
\lips
\subsection{Integrity Requirements}
\lips
\subsection{Privacy Requirements}
\lips
\subsection{Audit Requirements}
\lips
\subsection{Immunity Requirements}
\lips

\section{Cultural Requirements}
\subsection{Cultural Requirements}
\lips

\section{Compliance Requirements}
\subsection{Legal Requirements}
\lips
\subsection{Standards Compliance Requirements}
\lips

\section{Open Issues}
\lips

\section{Off-the-Shelf Solutions}
\subsection{Ready-Made Products}
\lips
\subsection{Reusable Components}
\lips
\subsection{Products That Can Be Copied}
\lips

\section{New Problems}
\subsection{Effects on the Current Environment}
\lips
\subsection{Effects on the Installed Systems}
\lips
\subsection{Potential User Problems}
\lips
\subsection{Limitations in the Anticipated Implementation Environment That May
Inhibit the New Product}
\lips
\subsection{Follow-Up Problems}
\lips

\section{Tasks}
\subsection{Project Planning}
\lips
\subsection{Planning of the Development Phases}
\lips

\section{Migration to the New Product}
\subsection{Requirements for Migration to the New Product}
\lips
\subsection{Data That Has to be Modified or Translated for the New System}
\lips

\section{Costs}
\lips
\section{User Documentation and Training}
\subsection{User Documentation Requirements}
User documentation will cover both the front-end and back-end features and functionalities.
\subsubsection{Back-End}
The backend user documentation will include all the API end points that are created. \newline
It will show the base URL for the end points along with descriptions of each
along with its required parameters and its types. These parameters will be those
in the path, query and body. The response from the API call will include what
the expected body will be along with any error handling. With this being a small
project, a rate limit section may be included to ensure that it does not exceed
the number of API calls. Versioning and support resources will be added for any
additional references missing. \newline
This document is intended to be passed on to the research lead or to any other
group who would like to understand how the back-end processes work along. It
will also be written such that someone else may use it to extend the current
functionalities or to troubleshoot any errors that may arise in the future after
this project has been passed on. 

\subsubsection{Front-End}
The front end documentation serves less as for developers but for the end user.
This documentation will include how to add new attributes to the data set, how
to request data plots and any major functionality features. \newline
This document is intended to be a help/tutorial for the end users who will be
using the site for its functionalities.

\subsection{Training Requirements}
No training is required to use the end product. 


\section{Waiting Room}
\lips

\section{Ideas for Solution}
\lips

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.  Please answer the following questions:

\begin{enumerate}
  \item What knowledge and skills will the team collectively need to acquire to
  successfully complete this capstone project?  Examples of possible knowledge
  to acquire include domain specific knowledge from the domain of your
  application, or software engineering knowledge, mechatronics knowledge or
  computer science knowledge.  Skills may be related to technology, or writing,
  or presentation, or team management, etc.  You should look to identify at
  least one item for each team member.
  \item For each of the knowledge areas and skills identified in the previous
  question, what are at least two approaches to acquiring the knowledge or
  mastering the skill?  Of the identified approaches, which will each team
  member pursue, and why did they make this choice?
\end{enumerate}

\end{document}