\begin{enumerate}
    \item What went well while writing this deliverable? \newline \newline
        When writing this deliverable, it was simple in a sense where many of
        the topics and ideas presented here were talked about before hand with
        both the team and the supervisors. It was more of a matter of expanding
        on ideas and topics in further detail to ensure that the problem and
        goals were aligned with previous conversations. This allowed the writing
        process to be more time consuming than actually being difficult. 
    \item What pain points did you experience during this deliverable, and how
    did you resolve them? \newline \newline
        The biggest pain point during this deliverable was figuring out how to
        properly explain the problem and goals. Many if not all ideas presented
        were simply ideas. It was quite difficult to be able to not only explain
        the goals but to also connect it back to why they are important to have
        in this project. Displaying the understanding of how pieces fit together
        and explaining why certain things are in scope was the most challenging
        part of this deliverable. 
    \item How did you and your team adjust the scope of your goals to ensure
    they are suitable for a Capstone project (not overly ambitious but also of
    appropriate complexity for a senior design project)? \newline \newline
        As a team, this was very much a concern in the beginning. This resulted
        in our team setting up strong measures of communication. Before even
        starting on this deliverable we made sure to go through each section
        with the supervisor. We had discussions throughout the meeting where the
        team brings a more technical point of view to aid in the supervisor's
        needs and wants. It was through this process that we did not have to
        adjust the scope of the groups goals much as we started with the a
        strong foundation and understanding with all parties involved.  
\end{enumerate}  